A Digital Library for Crowds on the Real-Time Social Web

### 2011-05-03 docs/csce_675/paper.tex
Added latex for paper.

\section{Crowd Discovery Algorithm}
\label{sec:crowd_algorithm}

The grouper deals with the transient crowd discovery and tracking in systems like Facebook and Twitter. For practical crowd discovery and tracking in a large time-evolving communication network, however, we face four key challenges:

>>>>

An architecture for the proposed solution is shown in Figure 1. The various modules of this architecture are as follows:

\begin{itemize}
  \item \noindent\textbf{Crawler}: This module deals with interacting with social media websites to collect information. For this project we will be collecting data from Twitter using Twitter Streaming APIs.
  \item \noindent\textbf{Filter}: This module removes unwanted data like spam messages, from data collected by the crawler.
  \item \noindent\textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS. 
  \item \noindent\textbf{HTTP JSON RESTful APIs}: This module will expose a HTTP-based API that clients can query to get data from the collection. The API will return crowds, users, and their tweets.
\end{itemize}

\begin{itemize}
  \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
   \item \noindent\textbf{Tornado}: Tornado is an open source, non-blocking web server.  We choose it because it is fast and scalable.
   \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database. We store the crowds discovered by the framework in this DB. The API module interacts with this database to retrieve collections as required by the user query.
\end{itemize}

\section{Crowd Discovery Algorithm}
\label{sec:crowd_algorithm}
The grouper deals with the transient crowd discovery and tracking in systems like Facebook and Twitter. For practical crowd discovery and tracking in a large time-evolving communication network, however, we face four key challenges:
